%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://www.blend360.com/}{Blend}} % Role
    {Data Analyst Trainee} % Organization
    {Colombia} % Location
    {February 2026 -- Present} % Dates
    {
      \begin{cvitems}
        \item {\textbf{Specialized training:} Selected Blend360 participant in applied data science.}
        \item {\textbf{ADRES model:} Collaborated in building and evaluating an intelligence model for the health sector, strengthening precision, traceability, and operational resilience in the review of claims and payments.}
        \item {\textbf{Digital transformation:} Participated in ML modeling and data visualization to support decision-making for a territorial entity.}
      \end{cvitems}
      \vspace{0.3em}
    }

  \vspace{0.6em}

%---------------------------------------------------------
  \cventry
    {\href{https://www.sas.com/en_us/home.html}{SAS Institute}} % Role
    {Analytics Assistant} % Organization
    {Bogotá, Colombia} % Location
    {May 2024 -- November 2024} % Dates
    {
      \begin{cvitems}
        \item {\textbf{Analytics presales support:} Built demos and proofs of concept, comparing SAS Viya Workbench vs. open-source solutions (e.g., Python) for technical discovery and business case solutions.}
        \item {\textbf{Materials and documentation:} Prepared notebooks, reports, and technical narratives for presentations, documenting workflows and best practices.}
      \end{cvitems}
      \vspace{0.3em}
    }

  \vspace{0.6em}

%---------------------------------------------------------
  \cventry
    {Escuela Colombiana de Ingeniería Julio Garavito} % Role
    {Academic and Administrative Teaching Assistant (Statistics Engineering)} % Organization
    {Bogotá, Colombia} % Location
    {2023 -- Present} % Dates
    {
      \begin{cvitems}
        \item {\textbf{Academic support:} Tutoring and guidance for students in core program courses, including problem-solving sessions and assignment reviews.}
        \item {\textbf{Administrative support:} Supported the program in organizing academic activities and events, logistics coordination, and communication with students.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
