%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

\raggedright

%-------------------------------------------------------------------------------
% SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Featured projects}

\begin{cvskills}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Saber 11 (ICFES)\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Sociodemographic performance analysis:} exploration, cleaning, and analysis of sociodemographic and institutional factors associated with scores, with visualizations and findings-oriented interpretation for decision-making.}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Linear regression\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Models with climate variables:} built and interpreted linear regression models to explain a response variable from climate covariates, including diagnosis of assumptions, outliers, and influence.}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}GLM Gamma + splines\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Nonlinear and weighted modeling:} fitted generalized linear models (Gamma) with splines and weighting, compared alternatives, and evaluated fit/interpretability for business scenarios.}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}DOE: Shiny + R package\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{App and package for experimental design:} developed a Shiny application and an R package for sample size calculation, aimed at use by non-technical users.}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}ICFES: AE + RF\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Final score prediction:} pipeline with autoencoders (latent representations) and Random Forest to estimate scores, with metric-based evaluation and latent variable analysis; developed in the context of projects with SAS and Python.}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Aeronautical regulations RAG\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Query system with LangChain/LangGraph:} ingestion of regulatory PDFs, embeddings, and vector search for contextual retrieval (RAG), with answer generation and source traceability.}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Psychological QA (LLMs)\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{QA assistant and quality evaluation:} prototype question-answering system with LLMs, focused on hallucination evaluation, answer quality control, and safety considerations.}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Veracity detection\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Sequential models with video:} extraction of facial features (OpenFace/LibreFace) and training of a BiLSTM model in PyTorch to classify temporal patterns associated with veracity/deception.}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}ARPRO\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Analytics for consumption vs. budget:} supported data analytics consulting for consumption and budget control and monitoring, information structuring, and modeling for forecasting and decision-making.}}

\end{cvskills}

%-------------------------------------------------------------------------------
% SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Other relevant projects}

\begin{cvskills}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Tax payment (IRS)\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Tax Data Analysis Demo:} Python demo notebook for preprocessing, visualization, and implementation of models that estimate tax payment probability with IRS-like data (Kaggle).}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Invoice automation (PDF)\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Text extraction and structuring:} automated information extraction from PDF invoices to generate clean and structured data; advanced cleaning and pattern detection to enable analytics and modeling.}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Bogotá mobility\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Descriptive analysis and findings:} participated in mobility data analysis focused on patterns and relationships to support exploration and decision-making (institutional source).}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}NHANES\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Data cleaning and quality:} cleaned and standardized variables, handled missing values, and validated consistency to enable reliable analysis in health surveys (NHANES).}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Insurance EDA\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Exploration and inference:} EDA on insurance data, construction of descriptive and inferential metrics, and generation of useful insights for risk and behavior analysis (Kaggle).}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Multivariate + Shiny\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Dimensionality reduction and clustering:} applied multivariate techniques (e.g., clustering and dimensionality reduction) and developed a Shiny app for interactive exploration of results (case: residential sectors in Switzerland).}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Frequentist vs. Bayes\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Methodological comparison:} contrasted frequentist and Bayesian inferential approaches on a standard case (Iris), with interpretation of results and assumptions.}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}DB modeling (Oracle)\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Design and implementation:} database modeling (UML) and implementation in Oracle SQL for an event scheduling/management system, with process and query automation.}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}NLP: Sentiment\end{minipage}}
    {\parbox[t]{0.72\linewidth}{\textbf{Sentiment analysis:} built a Python pipeline for preprocessing, vectorization, and sentiment analysis, with visualizations for executive-level reading of results (Kaggle).}}

  \cvskill
    {\begin{minipage}[t]{0.28\linewidth}Portfolio\end{minipage}}
    {\parbox[t]{0.72\linewidth}{Repositories: \href{https://github.com/RamiroSeb2021}{GitHub} \quad\textbar\quad Publications: \href{https://rpubs.com/juanayaramiro}{RPubs}}}

\end{cvskills}
